Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-05-31 docs/paper/paper.Rmd
streamline coverage plotting and plan text

```{r load-functions}
source(here("R", "utils.R"))
```

@@

```{r coverage}
ranges <- c(30, 60, 90)

coverage <- scores |>
  copy() |>
  DT(, horizon := as.character(horizon)) |>
  DT(, coverage_deviation := NULL) |>
  add_coverage(ranges = ranges, by = c("model", "horizon")) |>
  summarise_scores(fun = signif, digits = 2, by = c("model", "horizon")) |>
  melt(
    measure.vars = patterns("coverage_"), variable.name = "range",
    value.name = "coverage"
  )|>
  DT(, range := gsub("coverage_", "", range)) |>
  DT(, range := paste0(range, "% interval"))
```

@@

```{r vis-forecasts, fig.cap = "Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in the Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one to four weeks). Incidence rates are shown on a log scale. 30\\%, 60\\%, and 90\\% credible intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time.", out.width = "95%", fig.height = 12, fig.width = 9}
locs <- c("United Kingdom", "Germany", "Slovakia", "Italy", "Poland", "Greece")

forecasts[location_name %in% locs] |>
  DT(, date := target_end_date) |>
  plot_predictions(
    by = c("horizon", "location_name"), range = c(30, 60, 90)
  ) +
  facet_grid(
    location_name ~ horizon, scales = "free_y"
  ) +
  aes(fill = model, col = model) +
  scale_y_log10(labels = comma, oob = squish, limits = c(NA, NA)) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  labs(x = "Date", fill = "Model", col = "Model", ramp = "Range",
        y = "Notified test positive cases per 10,000 population")
```

@@

- Figure 3:
  Sub-figure 1:
    - Calibraton of forecasts by horizon and model
  Sub-figure 2:
    - Coverage of forecasts by quantile
  Sub-figure 3:
    - Relative interval score by quantile by horizon.

```{r plot-coverage, fig.height = 9, fig.width = 9, out.width = "95%"}
hlines <- data.table(
  range = paste0(ranges, "% interval"), nominal = ranges / 100
)

plot_cov_levels <- ggplot(coverage) +
  aes(
    x = horizon, y = coverage, colour = model, group = interaction(range, model)
  ) +
  geom_line() +
  geom_point() +
  geom_hline(
    data = hlines, aes(yintercept = nominal, x = NULL), linetype = "dashed"
  ) +
  scale_colour_brewer(palette = "Dark2") +
  scale_y_continuous(labels = percent) +
  facet_wrap(vars(range), ncol = 1, scales = "free_y") +
  theme_scoringutils() +
  labs(
     y = "Proportion of data within forecast interval",
     x = "Forecast horizon (weeks)",
     col = "Model"
  )

plot_cov_quantile <- scores |>
  summarise_scores(by = c("model", "quantile", "horizon")) |>
  plot_quantile_coverage(scores) +
  aes(col = model) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(labels = percent) +
  scale_colour_brewer(palette = "Dark2") +
  guides(col = guide_none()) +
  facet_wrap(vars(horizon)) +
  labs(col = "Model", y = "Percent of observations below quantile")

plot_interval_score <- relative_interval_score |>
  copy() |>
  DT(,
    .(relative_interval_score = median(relative_interval_score)),
    by = c("horizon", "range")
  ) |>
  ggplot() +
  aes(x = range / 100, y = relative_interval_score, col = as.factor(horizon)) +
  geom_hline(yintercept = 1, linetype = 2) +
  geom_point(size = 1.2) +
  geom_line(alpha = 0.8) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(trans = "log", breaks = seq(1, 4, by = 0.2)) +
  scale_colour_brewer(palette = "Accent") +
  theme_scoringutils() +
  labs(
    x = "Quantile", y = "Median relative interval score",
    col = "Forecast horizon (weeks)"
  )

(((plot_cov_levels /
  plot_interval_score)  +
  plot_layout(heights = c(3, 1), guides = "collect")
) |
  plot_cov_quantile) +
  plot_layout(guides = "collect", widths = c(1, 2)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.box="vertical", legend.margin = margin()
  )
```

>>>>

```{r load-functions}
source(here("R", "utils.R"))
source(here("R","coverage-plots.R"))
```

@@

```{r eval-parameters}
locs <- c("United Kingdom", "Germany", "Slovakia", "Italy", "Poland", "Greece")
ranges <- c(30, 60, 90)
```

```{r coverage}
coverage <- scores |>
  copy() |>
  DT(, horizon := as.character(horizon)) |>
  DT(, coverage_deviation := NULL) |>
  add_coverage(ranges = ranges, by = c("model", "horizon")) |>
  summarise_scores(fun = signif, digits = 2, by = c("model", "horizon")) |>
  melt(
    measure.vars = patterns("coverage_"), variable.name = "range",
    value.name = "coverage"
  )|>
  DT(, range := gsub("coverage_", "", range)) |>
  DT(, range := paste0(range, "% interval"))
```

@@

- Forecast performance overview for the ensemble and surrogate.
- Forecast performance overview by forecast horizon. Highlight degrading performance with this impacting the surrogate model to a greater degree. 
- Discussion country level differences in perforamance and link to potential growth rate trends.

```{r vis-forecasts, fig.cap = "Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in the Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one to four weeks). Incidence rates are shown on a log scale. 30\\%, 60\\%, and 90\\% credible intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time.", out.width = "95%", fig.height = 12, fig.width = 12}
plot_forecasts(forecasts, locs, ranges)
```

@@

- Calibration of forecasts at credible ranges of interest.
- Calibration across quantiles
- Relative interval scores by quantile

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%"}
(
  (
    (
      plot_coverage_range(coverage, ranges) /
        plot_rel_score_by_quantile(relative_interval_score)
    )  +
    plot_layout(heights = c(3, 1), guides = "collect")
  ) |
  plot_coverage_quantiles(scores)
) +
  plot_layout(guides = "collect", widths = c(1, 2)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin()
  )
```
